\section{Quantitative model and calibration}\label{sec:model}

The previous section shows that there is no role for labor income taxation in the optimal policy. However, the model abstracts from endogenous growth. When growth is endogenous, carbon taxes may be used to target the allocation of research across sectors as discussed in \cite{Acemoglu2012TheChange}. Then, a motive for income taxation may arise from optimal emission mitigation because the carbon tax deviates from implementing the efficient share of fossil production. 
Therefore, Section \ref{sec_quantmod} extends the core model to a quantitative framework mainly building on \cite{Fried2018ClimateAnalysis}. Section \ref{sec:calib} calibrates the quantitative model. 

\subsection{Quantitative model}\label{sec_quantmod}
%Either, if the carbon tax is set to decrease fossil research, the labor income tax


The main extensions to the core model is endogenous growth, a third non-energy sector, and skill heterogeneity to capture a skill bias in the green sector \citep{Consoli2016DoCapital}. 
%The neutral good is combined with an energy good to form  the final output good. The energy good consists of the dirty, fossil good and green good. The representative household provides two skills: high and low which are used in different shares in the neutral, fossil, and green sector. This extension serves to capture a that the green sector relies more on high-skill labor \citep{Consoli2016DoCapital}.
% Endogenous growth is modeled in form of directed technical change resulting from research enhanced by knowledge spillovers. 
The government maximizes utility of the representative household under the constraint of meeting an exogenous emission limit. This limit attaches social costs to fossil production and replaces the utility costs of fossil production in the core model. 
Appendix \ref{app:quant_mod} provides an overview of all equations determining competitive equilibrium.
%I study the model for a fixed amount of periods as I do not want to make any assumption on steady growth due to the absolute constraint on fossil production. 

\paragraph{Households}
% the rep agent
Modeling the economy as a representative family allows to abstract from inequality as a motive for government intervention while being able to study skill heterogeneity.
The household chooses hours of high-, $h_{ht}$, and low-skill workers, $h_{lt}$, hours of scientists, $S_t$, and average consumption, $C_t$, taking prices as given. The share of worker types is fixed with a lower share of high-skill workers, $z_h$, resulting in a skill premium. The household's problem remains static. The total time endowment of workers and scientists is given by $\bar{H}$. %Each period, it behaves according to: % The household's problem reads
The household receives lump-sum transfers from the government: $T_{\pi t}$ and $T_{lst}$ resulting from confiscating firm profits and the carbon tax, respectively.

%Scientists, $S_t$, form part of the household. Their size is normalized to one. At the beginning of a period,  the representative household supplies scientists treating their income as part of the household budget. However, to facilitate notation, scientists' income is confiscated by the government. This is not anticipated by the household.\footnote{\ Since firm profits are likewise confiscated by the government, firm profits, scientists income, and the subsidy on machine producers cancel from the government consolidated budget. The market imperfection arising from monopolistic competition is corrected for in a non-}
\begin{align*}
\underset{C_{t}, h_{lt}, h_{ht}, S_t}{max}&
u(C_{t}, h_{lt}, h_{ht}, S_t)\\
s.t.& \ \ p_{t}C_{t}\leq% (1-\tau_{\iota t})(h_{ht}w_{ht}+h_{lt}w_{lt})+T_t\\ 
z_h\lambda_t \left(h_{ht}w_{ht}\right)^{1-\tau_{\iota t}}+(1-z_h)\lambda_t\left(h_{lt}w_{lt}\right)^{1-\tau_{\iota t}}+w_{st}S_t+T_{\pi t}+T_{lst},\\
\ & h_{ht}\leq \bar{H},\ \hspace{2mm} h_{lt}\leq \bar{H},\ \hspace{2mm}  S_{t}\leq \bar{H}.
\end{align*}



The government levies a non-linear tax on income at the skill level. 
%The tax schedule is characterised by  a scaling factor, $\lambda$, and a parameter determining the progressivity of the tax schedule, $\tau_{\iota t}$, \citep[compare, e.g.,][]{Heathcote2017OptimalFramework}. The household receives lump-sum transfers from the government, $T_t$.  As $\tau_{\iota t}$ increases, the elasticity of disposable income with respect to hours worked decreases. 
The effect of a change in tax progressivity, $\tau_{\iota t}$, through lower income is similar across skill types. The substitution effect, in contrast, is higher for high-skill workers due to the family structure of the household side.
There are two reasons, first, the effect of tax progressivity on the after-tax wage rate is heterogeneous. Post-tax income falls more the higher pre-tax income as progressivity rises. 
Second, I assume a constant Frisch elasticity of hours with respect to the wage rate. Hence, the responsiveness of labor with respect to the after-tax wage rate varies with hours worked.\footnote{\ The percentage change in hours by high- and low-skilled workers to a percentage change in the wage rate is equivalent. Then, more hours worked initially imply a stronger reduction in absolute terms in response to a percentage change in the wage rate. }
Intuitively, a marginal rise in leisure is more valuable to workers which work more hours prior to the change in the wage rate. Therefore, as the post-tax return to labor falls, high-skill workers decrease their time spent working more.
Overall, the high-to-low skill ratio declines. 
%This modeling choice facilitates notation. 
%\begin{align}
%\underset{s_{jt}}{\max}\ \ & w_{jst}s_{jt}-\chi_s \frac{s_{jt}^{1+\sigma_s}}{1+\sigma_s}
%\end{align}

%I assume that all income from science is confiscated by the government to again facilitate notation. The assumption that scientists are risk neutral, introduces an additional externality as scientists do not internalise the social value of their research on society which is shaped by the shadow value of income. The advantage of this specification is that it prevents income tax parameters to affect the supply of scientists allowing to focus on the supply of hours by workers and consumption as the channels through which income taxes affect emissions. \tr{But it would be efficient. } 

%The choice to focus on a representative family enables to abstract from inequality as a motive for government intervention. 
\paragraph{Production}
Production carbon-tax-onlys into final good production, energy production, intermediate good production, and the production of machines and the intermediate labor input good. 
The final good producing sector is perfectly competitive combining the non-energy and energy goods according to:
\begin{align*}
Y_t=\left[\delta_y^\frac{1}{\varepsilon_y}E_{t}^{\frac{\varepsilon_y-1}{\varepsilon_y}}+(1-\delta_y)^\frac{1}{\varepsilon_y}N_{t}^{\frac{\varepsilon_y-1}{\varepsilon_y}}\right]^\frac{\varepsilon_y}{\varepsilon_y-1}.
\end{align*} 
I take the final good as the numeraire and define its price as $p_t=\left[\delta_yp_{Et}^{1-\varepsilon_y}+(1-\delta_y)p_{Nt}^{1-\varepsilon_y}\right]^{\frac{1}{1-\varepsilon_y}}$.
Energy producers perfectly competitively combine fossil and green energy to a composite energy good:
\begin{align*}
E_t=\left[F_t^\frac{\varepsilon_e-1}{\varepsilon_e}+G_t^\frac{\varepsilon_e-1}{\varepsilon_e}\right]^\frac{\varepsilon_e}{\varepsilon_e-1}.
\end{align*}
The price of energy is determined as  $p_{Et}= \left[(p_{Ft}+\tau_{Ft})^{1-\varepsilon_e}+p_{Gt}^{1-\varepsilon_e}\right]^\frac{1}{{1-\varepsilon_e}}$.



The government levies a sales tax per unit of fossil energy bought by energy producers. This tax is referred to as environmental, corrective, or carbon tax. 

Intermediate goods, fossil, $F_t$, green, $G_t$, and non-energy, $N_t$, are again produced by competitive sectors using a sector-specific labor input good and machines. The production function in sector $J\in \{F,G,N\}$ reads
\begin{align*}
&J_{t}= L_{Jt}^{1-\alpha_J}\int_{0}^{1}A_{Jit}^{1-\alpha_J}x_{Jit}^{\alpha_J} di.
\end{align*}
$A_{Jit}$ indicates the productivity of machine $i$ in sector $J$ at time $t$: $x_{Jit}$. 
Labor shares are sector specific. 
 %A reduction in labor supply, however, does not affect the structure of the economy due to free movement of labor. Importantly, \cite{Fried2018ClimateAnalysis} finds a higher labor share in the fossil sector.Therefore, the green sector cannot profit as much from an increased labor supply as fossil production reduces. This effect mitigates the effectiveness of a carbon tax. 
% as the price for the fossil good increases, demand for fossil reduces. Since the two goods are substitutes, demand for green energy increases. 
Intermediate good producers maximize profits: 
\begin{align*}
\pi_{Jt}=p_{Jt}F_t-w_{lJt}L_{Jt}-\int_{0}^{1}p_{xJit}x_{Jit}di,
\end{align*}
where $w_{lJt}$ is the price for the sector J's labor input good, and $p_{xJit}$ denotes the price of machines from producer $i$ in sector J. 

The labor input good of sector $J$, $L_{Jt}$, is produced by a perfectly competitive labor industry according to: 
\begin{align*}
L_{Jt}=h_{hJt}^{\theta_J}h_{lJt}^{1-\theta_J}.
\end{align*}
This additional intermediate industry allows to capture differences in skills by sector and in particular the skill bias of the green sector: $\theta_G>\frac{1}{2}(\theta_F+\theta_N)$. 

Machine producers are imperfect monopolists. They choose the price at which to sell their machines to intermediate good producers and decide on the amount of scientists to employ. Demand for machines increases with their productivity; this provides the incentive to invest in research. Irrespective of the sector, the costs of producing one machine is set to one unit of the final output good \citep[similar to][]{Fried2018ClimateAnalysis, Acemoglu2012TheChange}. 
Following the same literature, machine producers only receive returns to innovation for one period. Afterwards, patents expire. 
Each period, machine producer $i$ solves
\begin{align*}
\underset{p_{xJit}, s_{Jit}}{\max}&p_{xJit}(1+\zeta_{Jt})x_{Jit}-x_{Jit}-w_{st}s_{Jit},
\end{align*}
internalizing demand for machines. 
The government subsidizes machine production by $\zeta_{Jt}$ to correct for the monopolistic structure. Machine producers' profits are confiscated by the government to simplify notation.

\paragraph{Research and technology}
Technology growth is driven by research and spillover effects. The marginal product of research determines the amount of researchers employed.
The law of motion of technology of machines from firm $i$ in sector $J$ is modeled as
\begin{align*}
A_{Jit}=A_{Jit-1}\left(1+\gamma\left(\frac{s_{Jit}}{\rho_J}\right)^\eta\left(\frac{A_{t-1}}{A_{Jt-1}}\right)^\phi\right).
\end{align*}
The aggregate technology level is defined as
\begin{align*}
A_{Jt}=\int_{0}^{1}A_{Jit}di,\\
A_{t}=\frac{\rho_FA_{Ft}+\rho_GA_{Gt}+\rho_N A_{Nt}}{\rho_F+\rho_G+\rho_N}.
\end{align*}
The parameters $\rho_J$ capture the number of research processes by sector. This ensures that returns to scale refer to the ratio of scientists to research processes \citep{Fried2018ClimateAnalysis}. 
The number of research processes is highest in the non-energy sector. Therefore, a reduction in non-energy technology is more costly for growth in other sectors via knowledge spillovers. 
In the baseline calibration, $\eta$ is smaller unity implying diminishing returns to research within a sector following \cite{Fried2018ClimateAnalysis}. 
The private benefits of research for machine producers diverge from the social benefits as  producers neither observe the effect of today's research on tomorrow's productivity nor the positive knowledge spillovers for all research sectors captured by the term $\left(\frac{A_{t-1}}{A_{Jt-1}}\right)^\phi$ with $\phi>0$. There are no knowledge spillovers when $\phi=0$.

The marginal return to research in equilibrium is  given by
\begin{align}
w_{st}= \frac{\eta \gamma \left(\frac{A_{t-1}}{A_{Jt-1}}\right)^\phi (1-\alpha_J)\alpha_Js_{Jt}^{\eta-1}p_{Jt}J_t}{\rho_J^\eta}.
\end{align}
Ceteris paribus, revenues are increasing in labor supply which is affected by the income tax. The parameter $\gamma$ refers to research productivity.

The supply of scientists is endogenous in my model. With this choice, I depart from the standard assumption of a fixed supply of scientists in the literature on directed technical change \citep{Acemoglu2012TheChange, Fried2018ClimateAnalysis}.  Modeling the supply of researchers flexibly gives more freedom for the planner to choose lower growth levels: no a-priori fixed amount of research has to be employed. In light of an absolute emission limit, this could be important.
There is free movement of scientists across sectors, which seems reasonable given the duration of one period is 5 years and certain research skills are similar across sectors. %Furthermore, I do not assume free movement of scientists which simplifies the numeric calculation when the marginal gains of science diverge. 


When returns to science are decreasing, $\eta<1$, then there will always be research in the economy and no-growth is not a solution. Market forces increase the marginal returns from research to infinity as the number of scientists approaches zero. Thus, under such a parameter choice, fossil technology continues to grow. To satisfy the emission limit, fossil labor and machine usage have to decline towards zero. 
Furthermore, this parametric choice makes a smooth distribution of researchers across sectors beneficial. 

\paragraph{Effect of labor income taxation on research}
We are now equipped to discuss the effect of the labor income tax on the direction and level of research. As regards the level, a subsidy on labor, i.e. $\tau_{\iota t}<0$, makes households eager to supply more labor. As more labor is available to work with new technologies, returns to research in all sectors increase. Skill-heterogeneity introduces compositional effects of labor income taxation which I will discuss next. 

The model treats clean and dirty production processes as substitutes. As known from the literature on directed technical change, when the green and fossil energy alternatives are sufficient substitutes, then a market size effect - which directs research towards the sector with the bigger market of input goods - outweighs a price effect which would incentivize more research in the sector with scarcer input goods \citep{Hemous2021DirectedEconomics}. Hence, with green and fossil energy being sufficiently exchangeable, a reduction in the high- to low-skill ratio fosters fossil innovation and increases emissions. 

On the other hand, the model features complementarity of non-energy and energy goods in the final production function. Innovation in the non-energy sector can be perceived as energy-saving technology advances. Since the non-energy sector is more low-skill intense than the energy composite, a drop in the ratio of high to low skill increases the relative size of the market for non-energy input goods. However, since energy and non-energy goods are complements, the lower price of non-energy goods may dominate and direct innovation towards the sector with the scarcer input good; that is, energy.
Both mechanisms enhance fossil innovation as tax progressivity rises. 
% NOTE: it is true for the progressive income tax that the price effect dominates and research transitions to the energy sector! It was for the carbon tax that knowledge spillovers are pivotal. 


%Since the aggregate level of research inputs is endogenous, the factors which determine the direction of innovation in other models, also determine the quantity of research demanded in my model. For example, when labor supply in general reduces, a market size effect curbs demand for research in all sectors. %One can show that a regressive income tax is used to boost the supply of research if demand is inefficiently low overall.

%Yet, in equilibrium, this fall in demand is absorbed by changes in the wage rate. Scientists are willing to work the same amount at the lower wage rate since the utility of consumption rises as workers work less.


%\tr{What is the effect on prices?}
%Then input shares across sectors are not constant. 

  
\paragraph{Markets}
In equilibrium, markets clear. I explicitly model markets for skill, scientists, and the final consumption good:
\begin{align*}
z_h h_{ht}&=h_{hFt}+h_{hGt}+h_{hNt},\\
(1-z_h) h_{lt}&=h_{lFt}+h_{lGt}+h_{lNt},\\
S_t&=s_{Ft}+s_{Gt}+s_{Nt},\\
C_t&=Y_t-\int_{0}^{1}\left(x_{Fit}+x_{Git}+x_{Nit}\right)di.  %-Gov_t.
\end{align*}
%The government does not redistribute environmental tax revenues and instead consumes the final output good captured by $Gov_t$. 

\paragraph{Government}

The government seeks to maximize lifetime utility of the representative household. Each period, the government is constrained by an emission limit, $\Omega_t$, in line with the Paris Agreement.  
It is characterized as a Ramsey planner taking the behavior of firms and households as given and discounting utility by the household's time discount factor, $\beta$.
The planner chooses time paths for environmental taxes and the tax progressivity parameter on the income tax scheme to solve:%\footnote{\ I code the planner's problem using a primal approach going back to \cite{Lucas1983OptimalCapital} where prices and tax instruments are replaced by equilibrium equations describing the competitive equilibrium. It is straight forward to show that the Ramsey allocation is a competitive equilibrium allocation when prices and taxes are chosen adequately.}
\begin{align}
\underset{\{\tau_{Ft}\}_{t=0}^{\infty},\{\tau_{\iota t}\}_{t=0}^{\infty}}{\max}&\sum_{t=0}^{\infty}\beta^t u(C_{t}, h_{ht}, h_{lt}, S_t)%-\chi_s\frac{s_{ft}^{1-\sigma_s}}{{1-\sigma_s}}-\chi_s\frac{s_{gt}^{1-\sigma_s}}{{1-\sigma_s}}-\chi_s\frac{s_{nt}^{1-\sigma_s}}{{1-\sigma_s}}
\nonumber \\
s.t.\ %& (1)\  \tau_{\iota t}(h_{ht}w_{ht}+h_{lt}w_{lt})=T_t\  \forall \ t\geq 0\\
&  \omega F_{t} -\delta \leq \Omega_t, \label{eq:emslim} % \ \hspace{3mm} \forall t \in\{0,T\}, 
\\ %\hspace{3mm} \text{(emission target)}\\
&  z_h\left(w_{ht}h_{ht}-\lambda_t \left(w_{ht}h_{ht}\right)^{1-\tau_{\iota t}}\right)+(1-z_h)\left(w_{lt}h_{lt}-\lambda_t\left(w_{lt}h_{lt}\right)^{1-\tau_{\iota t}}\right)=0, \label{eq:incbud}\\
&  \sum_{J\in\{F,G,N\}}\left(\int_{0}^{I}\pi_{Jit}di-\zeta_{Jt}\int_{0}^{I}p_{Jixt}x_{Jit}di\right) = w_{st}S_t= T_{\pi t},\label{eq:profbud}\\ 
&  \tau_{Ft}F_{t}=T_{lst}.\label{eq:envbud}
\end{align}

%- emission constraint
Constraint \eqref{eq:emslim} is the emission limit. The parameter $\delta$ captures the capacity of the environment to reduce emitted CO$_2$ through sinks, such as forests and moors.  The parameter $\omega$ determines  CO$_2$ emissions per unit of fossil energy produced. I abstract from other greenhouse gases. This keeps the model simple while accounting for the pollutant the most relevant for mitigation policies.\footnote{\ CO$_2$ dominates total greenhouse gas forcing \citep[p.29]{IPCC2022}, and other greenhouse gasses hold a smaller mitigation potential (p.26).}

%- gov budgets
The scale parameter on income taxes, $\lambda_t$, adjusts so that all revenues from the labor income tax are redistributed to the household, eq. \eqref{eq:incbud}.
The government also generates revenues from confiscating profits which are used to finance the subsidy on machine production. The rest is rebated lump sum to households, eq. \eqref{eq:profbud}. 
Finally, the government redistributes environmental tax revenues lump sum, eq. \eqref{eq:envbud}.

%\paragraph{Setup of problem: focus on current population; continuation value}
