
\section{Introduction}
The public finance literature has focused the discussion of optimal labour income taxation and the degree of progressivity on the equity-efficiency trade-off.  The benefits of labour taxes arise from redistribution. With concave utility specifications full redistribution is efficient. However, the optimal tax system does not feature full redistribution when labour supply is endogenous. Instead, the degree of redistribution is traded-off against aggregate output as individuals reduce their labour supply in response to the labour income tax. 

\paragraph{An environmental perspective}

 Adding environmental externalities to the classical public finance framework changes the light with which efficiency costs are perceived. Instead of merely reducing welfare, direct benefits through externality reduction arise by lowering output. 
Yet, in general, in the presence of corrective tax instruments and the assumption of a clean alternative, %which direct production to a non-polluting alternative, however,
distortionary labour taxes are not employed as environmental policy instruments.\footnote{ Compare my paper on Sustainable production and demand where there is no limit/ no disaster.} 
However, technological progress might not suffice to meet climate targets while leaving per capita consumption (growth) unchanged. This is especially relevant given the tight time frame foreseen by the Paris Agreement.\footnote{\ Here, ratifying states have agreed on limiting temperature rises to well below 2°C and preferably 1.5°C and to achieve climate neutrality by mid-century \url{https://unfccc.int/process-and-meetings/the-paris-agreement/the-paris-agreement}. } Indeed, in their IPCC report, \cite{Rogelj2018MitigationDevelopment.} advocate additional demand-side measures to lower demand for energy and greenhouse gas intense products (p.97 bottom) to meet agreed-on climate targets.\footnote{\tr{ I am unsure if distortionary taxes would indeed arise as an optimal environmental policy tool when corrective taxes are available. Corrective taxes could be used... Maybe need some other argument, e.g. not available, why?; some political argument; inequality might be another if poor households consume a bigger polluting share; Changing already established policy measures less difficult than introducing ne taxes?...I would make this framing dependent on the findings. I guess tax progressivity could lower consumption of consumption-rich households in particular which could contain some sort of advantage. A general consumption tax might serve as a baseline corrective tax and the explicit corrective tax accounts for the gap between the vat consumption tax and the social cost of the dirtier sector. }}

%\paragraph{Consumption reduction (degrowth!)}
% 
% Growth drag may result in papers which study the trade-off between consumption growth and the environment \citep{Acemoglu2012TheChange, Stokey1998AreGrowth, Jones2016LifeGrowth}. %\citep{Rockstrom2009AHumanity}\footnote{\ In their article, \cite{Rockstrom2009AHumanity} argue that several planetary boundaries have already been surpassed. Uncertainties about their interaction are another argument in favour of more cautious environmental policies. } such as biodiversity and nitrogen xxx.
%Taken this broader view on environmental pollution through economic activity, it becomes more questionable, if a perfectly clean technology exists or can ever be innovated.  

%In sum, the need to reduce environmental externalities rather quickly and the potential non-existence of perfectly green technologies could make it optimal to use classical fiscal tax instruments for environmental concerns through the efficiency channel. 

%\textit{So far: efficiency-equity channel; plus on efficiency side}
\paragraph{Trade-offs: environmental externality} Consumption reduction in affluent countries has also been promoted by some (non-economic) scholars \citep{Schor2005SustainableReduction, Pullinger2014WorkingDesign, Arrow2004AreMuch}. But, the general equilibrium effects are less well understood.
While having an advantageous direct effect on the externality, counteracting indirect effects arise in a general equilibrium framework. Proponents of a reduction policy especially focus on consumption by the rich which consume a higher amount of natural resources.\footnote{\ Note Sonja: Abstracting from inequality, would it still be best to reduce consumption by the rich when the poor have a higher marginal propensity to consume dirty? \textit{Could be an important aspect in the model}.}
This concern could add to the benefits of tax progressivity.
However, targeting these households in particular for environmental reasons, in contrast, will lower the supply of high skilled labour.\footnote{\ The relation of labour tax progressivity and skill investment has been studied by \cite{Heathcote2017OptimalFramework}.} Yet, these skills are essentially important in green sectors of the economy \citep{Consoli2016DoCapital}. As a result, dirty production becomes relatively cheaper and the dirty share of production rises. 

%The literature on optimal environmental policy knows the 
Furthermore, the direction of technological change might be drawn towards the more polluting good in response to a higher progressivity. The reduction in the cleaner sector's labour input good diminishes the relative market size of this sector. The market effect shifts innovation towards the bigger dirty sector. On the other hand, the higher price of cleaner products makes innovation in this sector more profitable, the price effect. 
One contribution of the paper is to discuss optimal fiscal policy in an endogenous growth setting. 


\paragraph{Research question}
Given these counteracting forces, this paper seeks to answer whether a more progressive labour tax is indeed optimal for environmental reasons. 
%\tr{Why not use one corrective tax in each sector? Political argument? }
\\

\noindent\rule[1ex]{\textwidth}{1pt}
\paragraph{The below is an addendum in case I want to add capital taxation somewhere...} \tr{below relatively close to \cite{Conesa2009TaxingAll}} 
Another prominent debate in the public finance literature centres on the optimal size of the capital tax. The optimality of zero capital taxation has been argued for in the seminal work by Judd (1985) and affirmed by others.  However, as discussed by \cite{Conesa2009TaxingAll}, the optimality of a zero capital tax hinges upon the endogeneity of labour supply. The capital tax rises when allowing for life-cycle aspects. In this setting, it is optimal to tax capital heavily and to accept a reduction in consumption at a modest reduction of hours worked for the benefit of better insurance and redistribution. Taking environmental externalities into account, the optimal capital tax may even be higher due to its advantageous effect on the externality.

\cite{Domeij2004OnTaxes} discuss a reduction of capital taxes in a model with idiosyncratic productivity shocks which imply  wealth inequality. Their focus rests on the distributional effect which arise in the transition from the benchmark to a lower capital tax. They find huge negative distributional effects over the transition since a linear labour tax is less progressive.  (\textit{check this}) The distributional effects outweigh the benefits of a higher capital stock and output. 

\tr{(I would first want to look at labour tax progressivity as I can build on the tractable model by \cite{Heathcote2017OptimalFramework}.)}
\\

\noindent\rule[1ex]{\textwidth}{1pt}

\paragraph{Empirical motivation}
The key channel inducing adverse consequences of a reduction policy on the externality hinges on the skill-bias in the cleaner sector. % and that consumption-rich households are high skill households. \ar that they are richer is an equilibrium effect 
For the US, \cite{Consoli2016DoCapital} find that within broader occupational groups greener occupations are skill-biased: on average, the degree of non-routine tasks is higher as are formal education, work experience, and on-the-job training. I link this evidence to the type of skills employed in the dirty and the cleaner sector in the model. %\ar might be able to abstract from CRRA utility function and to focus on the skill accumulation dimension...
% \cite{Bowen2018CharacterisingComposition} estimate a relatively low difference in skills between jobs and argue that this gap can be closed quickly by on-the-job trainings. 


\paragraph{Exercise}
In the first part of the paper, I study the effects of labour-tax progressivity  on the environmental externality in a tractable general equilibrium model with directed technical change. The model builds on \cite{Heathcote2017OptimalFramework} and \cite{Acemoglu2012TheChange}. 
In contrast to \cite{Heathcote2017OptimalFramework}, I abstract from idiosyncratic risk and the life cycle component to focus on the medium to long run and the environment. 
The planner still faces the trade-off between equity and skill accumulation. 
In this part of the paper, I focus on conditions which shape the relation of production and the environment so that fiscal policies are employed for environmental reasons although corrective taxes are available.  
Secondly, I examine the optimal policy and transitions to the new steady state from a realistically calibrated current state of the economy and a quantitative model\footnote{\ For example, as in  \cite{Fried2018ClimateAnalysis} I add additional features to the innovation process such as spillovers across sectors and a third neutral sector of production.}.

% Two possible setups seem interesting. (1) The government maximises a \textit{(possibly pareto-weighted, utilitarian)} social welfare function. This version allows to account for other planetary boundaries potentially interacted with the dominant climate boundary and carbon emissions. (2)
The government chooses tax instruments to maximise a social welfare function constrained by the  emission targets consistent with the Paris Agreement.  The advantage of this approach is that it suffers less from  misspesification due to the uncertainty surrounding the environment and production. Furthermore, it is closely related to the current political debate. Compare appendix section \ref{app:emission_climate_targets} for a more in depth discussion of this aspect.  

I study different specifications of the social welfare function: (1) a Utilitarian, (2) the variance of reductions in consumption welfare across households which is meant to proxy for social tension, and (3) the objective function minimises the consumption reduction of the most affected group similar in vein to a Rawlsian criterium. \tr{(I will start to code the Utilitarian version and only add (2) and (3) if necessary, i.e., tax progressivity is unaffected by the environmental constraint.)}
%(\textit{\textbf{Note:}}(3) A reduction policy can also become optimal when climate policies as required to meet the targets are socially unfeasible. For example, poor households consume a higher share of polluting goods, reducing overall consumption through labour taxes, instead, could be more favourable in terms of inequality. )

I perform two quantitative experiments to scrutinise the contribution of directed technological change and skill heterogeneity on the optimal policy. First, I rerun the analysis in versions of the model where either or both channels are shut down.  Second, I introduce the optimal policy of the amended model, e.g. the  version without skill heterogeneity, into the model with skill heterogeneity to learn how skill heterogeneity shapes the effect of the optimal policy on the externality.

\paragraph{Sensitivity}
First, I adjust the model for different specifications of the skill accumulation process which is essential in shaping the adverse effects of reduction policies on the environment.\footnote{\ For example, skill can be modelled as generating intergenerational spill-overs within households as in \cite{Borissov2019CarbonDevelopment}.} Second, I change the specification of utility functions which incorporates the arguments put forward by advocates of reduction policies such as: habits, social preferences which even absent an environmental externality imply overconsumption, and social effects of leisure \textit{(or one of these)}.  These extensions all add to the benefits of reducing consumption. Third, instead of fiscal policies the government has a policy tool to lower the maximum hours worked per worker and period. Such a policy is closer to what proponents of a reduction policy suggest. % Third, more evolved modelling of the innovation process as in \cite{Fried2018ClimateAnalysis} is introduced \textit{(add this to the main quantitative part)}. 

\paragraph{Literature}
\begin{itemize}
\item Public finance literature on optimal labour tax (progressivity) or capital tax (advantage of labour tax progressivity: there is a tractable model already available; capital tax with the zero capital tax finding seems interesting and important though...But requires a different model with capital) \citep{Heathcote2017OptimalFramework, Conesa2009TaxingAll, Domeij2004OnTaxes}
\item Optimal environmental policy with and without directed technical change \citep{Acemoglu2012TheChange, Acemoglu2016TransitionTechnology, Fried2018ClimateAnalysis, Barrage2019OptimalPolicy, Golosov2014OptimalEquilibrium, Hassler2016EnvironmentalMacroeconomics}
\item potentially: limits to growth \citep{Stokey1998AreGrowth, Jones2016LifeGrowth, Arrow2004AreMuch}
\item building on the following literature: \begin{itemize}
\item skills and green production: empirical \citep{Consoli2016DoCapital, Bowen2018CharacterisingComposition, Borissov2019CarbonDevelopment}; growth model with skill accumulation \citep{Borissov2019CarbonDevelopment}
\item literature on the environment and limits to growth \citep{Dasgupta2021, Rockstrom2009AHumanity, Brock2005ChapterEmpirics, Arrow2004AreMuch, Cohen2019AnnualSubstitutable}
\item literature advocating reduction policies \citep{Schor2005SustainableReduction, Pullinger2014WorkingDesign}
%Some (non-economist) scholars argue for the necessity to reduce current consumption growth in developed economies due to threats to planetary boundaries \citep{Arrow2004AreMuch, Schor2005SustainableReduction}. 

\end{itemize}
\end{itemize}
